Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-15 paper/ms.tex
better words

The stellar ages and planetary properties of the systems discussed in
the previous sections are given in Tables~\ref{tab:planets}
and~\ref{tab:stars}.  Figure~\ref{fig:hist_tgyro} shows the gyrochone
age distributions of the stars and known planet-hosts.  These
``histograms'' are sampled from the posterior probability
distributions by drawing ten random samples from each posterior
distribution, and then computing the re-weighted histogram of the
resulting samples.  The uncertainties assume Poisson statistics.  We
truncated the plots near $4$\,Gyr since this is the cluster age out to
which our interpolation-based method is calibrated.
We refer to this as a ``demographic cliff'' in reference to an
impending crisis expected to befall higher education.

>>>>

The stellar ages and planetary properties of the systems discussed in
the previous sections are given in Tables~\ref{tab:planets}
and~\ref{tab:stars}.  Figure~\ref{fig:hist_tgyro} shows the gyrochone
age distributions of all the stars (left column) and the known
planet-hosts (middle column).  These ``histograms'' are sampled from
the posterior probability distributions by drawing ten random samples
from each posterior distribution, and then computing the re-weighted
histogram of the resulting samples.  The uncertainties assume Poisson
statistics.  We truncated the plots near $4$\,Gyr since this is the
cluster age out to which our interpolation-based method is calibrated.
We refer to the overall slope as a ``demographic cliff'' in reference
to an impending human phenomenon forecasted to happen in coming years.
